New title

### 2020-04-15 paper/SQJ-answers_to_reviewers.txt

====================
Associate Editor
====================

AE1: Other than answering the many punctual questions of the reviewers, I urge the authors to reconsider the way the current manuscript frames their contribution and novelty claims, since both reviewers express strong complains.

ANSWER: ?????

AE2: The concepts of diversity and diversity-awareness seem badly characterised. A reviewer complains that test transplantation and differential testing are techniques for test reuse and test oracles but defining them as diversity-aware techniques appears arbitrary, and distracts from understanding the actual contribution of the paper.

ANSWER: ?????

AE3: Another reviewer complains about the novelty of the findings, since it is known that test transplantation and differential testing can help to reveal bugs. Possibly the authors should partially downgrade or at least re-argue their novelty claims.

ANSWER: ?????

====================
Reviewer #1
====================

R1-1: This paper is well written and presents interesting experiments that exposed confirmed JS engine bugs.
The experiments are well designed and clearly explained.

ANSWER: Thank you.

*R1-2: My main criticism of this paper is the concept of "diversity" that the authors used to frame this work.
As stated in the paper this work has the objective to evaluate the importance of diversity to find functional bugs.
Claiming that test transplantation and cross-engine differential testing are "diversity-aware techniques" Why is that?
Test transplantation simply re-uses tests for one engine to test another engine, it does not make sure that the tests are different.
It just passively re-use tests without promoting diversity.
Differential testing compares the results of executing the same tests on different engines, it is not a diversity aware technique.
As such, the explanation in the introduction of why test transplantation and differential testing are diversity-aware is a bit artificial.
Moreover, the authors at page 2 stated that "this paper explores diversity of implementations and diversity of sources of test cases as opposed to diversity of the test cases themselves."
I think this creates an overload and confusion of the term diversity.
Framing the work on this concept of diversity is artificial and distracts the reader from the main objective of this paper: showing that test transplantation and differential testing can be useful in exposing bugs in JS engines.

ANSWER: ?????

R1-3: The technical contribution of this paper is not well stated, what are the challenges of applying test transplantation, fuzzy and differential testing for JS engines?

ANSWER: ?????

R1-4: Since the input of a JS engine is a JS program, why we need test transplantation or fuzzy generators? Why we cannot rely on a corpus of JS programs as tests?

ANSWER: ?????

R1-5: Page 3 line 24, please explain this sentence: "One possible reason is that it is still not practical to fully automate the technique."
why is not practical, what are the challenges of differential testing in this context?

ANSWER: ?????

R1-6: Page 4, some claiming in the key findings are not justified. Did you check if the tests implemented for different JS engines are really different? How to measure test diversity across different implementations? Again the concept of diversity is not clear in this paper.

ANSWER: ?????

R1-7: Page 6 line 40, why discard tests that require external libraries?

ANSWER: ?????

R1-8: Page 7 Section 4.1. Indeed, issue trackers contain many tests, but usually, these tests are added to the test suite for regression. Did you check if the tests extracted from the issue tracker were duplicates with the one in the test suite?

ANSWER: ?????

R1-9: Page 7 Lines 24 to 41. The NN to recognise ``code'' and ``non code'' is not well-motivated. Why don't just assume that all file is "code"? Since for differential testing, you will exclude those tests that fail on all engines, in this case, invalid inputs will be automatically ignored. Is this approach motivated? Is it really needed? Or all "non code" files will make all engine fails? Please provide empirical evidence that this extra step is needed.

ANSWER: ?????

R1-10: Page 7 It is also unclear why you use word2vec. Word2vec is used to measure the semantic similarity between two words. Word2vec analyzes a set of documents and trains a model that embeds words into a vector space, where words with similar semantics are close in the space. Why you need semantic similarity?

ANSWER: ?????

R1-11: Page 8 You mentioned that differential testing is challenging because a human need to inspect the differences? How you addressed the challenge? Do you address the challenge?

ANSWER: ?????

*R1-12: Page 9 I don't understand why you didn't mine JS programs from github, these would have yielded to a larger set of tests.

ANSWER: ?????

R1-13: Page 11 It is unclear why you ran the suite once a day for seven consecutive days and averaged the passing ratios. Why once a day? and why you do this? For detecting and avoid flakiness tests? Why you didn't run the tests 7 times the same day?

ANSWER: ?????

R1-14: Page 14 how did you decided FP and TP? One author or multiple authors of this paper participated in the labelling?

ANSWER: ?????

R1-15: Page 21 Given lesson 3) why you motivated the paper saying that differential testing is challenging? What are the technical challenges entailed by differential test JS engines that this paper address?

ANSWER: ?????

====================
Reviewer #2: 
====================

R2-1: Overall, the authors did non-trivial engineering work, conducted an interesting experiment, and made a good contribution to the open-source community by reporting those bugs.

ANSWER: Thank you.

*R2-2: However, as a scientific study, the key findings listed in Section 1 are not very novel:
1. It is not surprising to find some bugs if running a different set of test suites (with thousands of test cases) from a different engine.
2. Although the ECMAScript is very well-defined (most parts of the specification are pseudocode), it is also well-known that the specification does not define everything and that JavaScript engines vary in those undefined behaviors. Therefore, the results obtained in RQ1 are not novel.
3. "Differential testing is feasible on real, complex, widely used pieces of software." This is also not a novel finding. People have been using differential testing on C/C++ compilers and JVMs. The following paper is one example: Coverage-Directed Differential Testing of JVM Implementations [PLDI'16]

ANSWER: ?????

*R2-3: I think a more impactful contribution would be to categorize all those extracted test files and to release an open-source project that automates the testing techniques proposed in this paper on any JavaScript engine binary (e.g., Hermes, JerryScript, or Duktape, etc.).

ANSWER: ?????

R2-4: In Section 3, the paper claimed to have tested the Microsoft Chakra engine. However, I believe the authors meant the ChakraCore engine, which is the open-sourced variation of the Chakra engine. Moreover, Microsoft announced a year ago that the Edge browser will be based on Chromium. I believe ChakraCore is not being actively developed anymore. I understand that the experiment might be done a while ago. The paper should clarify the version number of JavaScript engines under test and document when the bug reports got confirmed.

ANSWER: ?????

R2-5: Facebook released Hermes, which is a JavaScript engine designed for ReactNative and mobile devices. It would be interesting to see how many bugs can be found on Hermes.

ANSWER: ?????

R2-6: Section 4 - The structure of this section could be improved. The authors should probably put the description of test cases from all engines in one subsection, and description of test files mined from issue tracker in a parallel subsection.

ANSWER: ?????

R2-7: "We did not consider tests from the Chakra repository because they dependent on non-portable objects". Please explain in detail and give an example of the non-portable objects.

ANSWER: ?????

R2-8: "This classifier is publicly available from our website as a separate component". Not sure which website the author is referring to. It would be great to provide a permanent link.

ANSWER: ?????

R2-9: Section 4.1 - The paper also mentioned that 1,240 JavaScript files are crawled from the issue tracker. Those files are used as test drivers in the experiment. How many bugs come from the issue tracker? If a bug is revealed by a file uploaded to the issue tracker, why the JavaScript engine maintainers didn't fix them in the first place?

ANSWER: ?????

R2-10: Section 5.1 - Is the test case in Figure 3 crawled from ChakraCore's codebase? Or is it revealed after a fuzzer mutates the argument of getView?

ANSWER: ?????

R2-11: Section 5.2 - How effective is the clusterization?

ANSWER: ?????

R2-12: Section 5.3 - The selection of fuzzer does not sound convincing to me. The authors mentioned that some fuzzers (e.g., AFL) are not used in the experiments because they produce test input that is not syntactically valid. However, they chose radamsa, which is a general-purpose fuzzer that may also produce syntactically invalid inputs.

ANSWER: ?????

R2-13: Section 6.1 - The ECMAScript conformance statistics of JavaScript engines are already publicly available on the Internet from multiple sources. Therefore, the findings in Section 6.1 are not novel. Moreover, JavaScript engines are evolving quickly, the manuscript should report date and engine versions associated with those conformance numbers.

ANSWER: ?????

R2-14: Section 6.2 - Since the authors mined test files from Duktape, JerryScript, JSI, and Tiny-js. It seems natural to run test transplantation on these engines, which may reveal more bugs. It would be good to explain why the authors did not do so.

ANSWER: ?????

R2-15: Since the manuscript is suggesting that test transplantation is effective for testing complex software. It would be great to quantify the manual work required to transplant tests (written in JavaScript) from one engine to another. For example, how many non-portable harness functions are mocked for each transplantation?

ANSWER: ?????

R2-16: Section 6.3 - Please provide a more detailed description of the configuration of the two black-box mutation fuzzers. How many valid and invalid inputs are generated by the fuzzers?
The description should also report the time spent in fuzzing and the number of machines (including hardware configuration) used for differential testing.

ANSWER: ?????

R2-17: In the first row of Table 7, the total number of "hi" warnings of JSC, V8, ChakraCore, and SpiderMonkey is only 626, while the "+1" column is 628, which is more than the total number of the previous columns combined. Please double-check the data.

ANSWER: ?????

R2-18: Section 7 looks more like a "Case Study" section instead of a "Discussion" section.
It would be interesting to analyze why test transplantation could reveal some bugs. Does each engine focus on testing different aspects? What kind of tests are more likely to expose bugs?

ANSWER: ?????

R2-19 (minor issues): Please clean up or use a consistent format for the following text:
"[Cleansing]" on line 40 of page 6.
"[Test Harness]" on line 46-47 of page 6.
"[Exploratory Phase.]" on line 23, page 16
"[Non-Exploratory Phase.]" on line 46-47, page 16
Ecmascript 6 -> "ECMAScript 6"
"well tested" -> "well-tested"

ANSWER: ?????

R2-20: The references use too many external links to websites, which may not be available in the next few years or decades.

ANSWER: ?????

### 2020-05-23 paper/abstract.tex
Revised the whole text and removed instances of diversity ou diversity-aware

\textbf{Context.} JavaScript is a very popular programming language today with several
implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the spec is intentionally
incomplete and evolves frequently.
\textbf{Objective.} This paper evaluates the importance of
diversity to find functional bugs in JavaScript engines. \textbf{Method.} For that, we
explored two existing diversity-aware techniques---test transplantation and
cross-engine differential testing. The first technique runs test
suites of a given engine in another engine. The second technique
fuzzes existing inputs and then compares the output produced by
different engines with a differential oracle.
\textbf{Results.} We considered engines from four major players in our
experiments--Apple, Google, Microsoft, and Mozilla. Our results
indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}. To summarize, our results show that
diversity-aware techniques are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.

>>>>

\textbf{Context.} 
JavaScript is a very popular programming language today with several
implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the spec is intentionally
incomplete and evolves frequently.
\textbf{Objective.} 
This paper investigates the use of test transplantation and differential testing
for revealing functional bugs in JavaScript engines.
The former technique runs test suites of a given engine on another engine. 
The latter technique fuzzes existing inputs 
and then compares the output produced by different engines with a differential oracle.
\textbf{Method.} 
We conducted experiments with engines from four major players
--Apple, Google, Microsoft, and Mozilla--to assess the effectiveness of 
test transplantation and differential testing.
\textbf{Results.} 
Our results indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}. 
To summarize, our results show that
test transplantation and differential testing
are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.

### 2020-05-23 paper/paper.tex
Revised the whole text and removed instances of diversity ou diversity-aware

\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head

@@

\begin{abstract}
  \input{abstract}
  \keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
\end{abstract}

@@

%% WHAT WE DID
This work, which is empirical in nature, reports on a study to evaluate the importance of diversity
to find bugs in JavaScript engines; it covers two complementary
diversity-aware testing techniques.

%\vspace{-1ex}
%noitemsep,
\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
\item \emph{Test transplantation} leverages diversity of test
  cases. This technique evaluates the effect of running test files
  written for a given engine in other engines. The intuition is that
  developers design test cases with different objectives in mind. As
  such, replaying these tests in different engines could reveal
  unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of
  engine implementations. This technique fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines.\Comment{ using a differential
    oracle.} The intuition is that interesting inputs can be created
  from existing inputs and multiple engines can be used to address the
  lack of oracles.
\end{itemize}

@@

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
to prior work on this topic, this paper explores diversity of
implementations and diversity of sources of test cases as opposed to
diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
elaborates related work on this topic. Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum up, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is empirical: 
we provide a comprehensive study analyzing the effectiveness of diversity-aware
techniques to find functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed. 
We reported a total of \totalBugsReported{} bugs. 
Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed. 
2)~An infrastructure for diversity-aware testing.
The scripts to run the experiments will be available upon request. 
The data is publicly available \dataRepo{}.

\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
that exploring diversity should be encouraged to find functional bugs
in JavaScript engines.

@@

The goal of this paper is to assess ability of techniques that
leverage diversity to find functional bugs
in \javascript\ engines. Based on that, we pose three questions:
\begin{description}[leftmargin=.5in]
\item[RQ1.] How conformant are the engines to the Test262 suite?
\item[RQ2.] How effective is test transplantation to find bugs?
\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
\end{description}

The first question focuses on the conformance of our selected engines
to the official Test262 suite~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. The second question
focuses on the effectiveness of test transplantation
(Section~\ref{sec:transplantation}). The rationale for using inputs
from different engines is that developers consider different goals
when writing tests---suites written for a given engine may cover
scenarios not covered by a different engine. The third question
evaluates the effectiveness of cross-engine differential testing to
find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale for this question is that fuzzing inputs may explore
scenarios not well tested by at least one of the engines.

@@

\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
three months of the study, our inspection process was exploratory.  In
this phase, we wanted to learn whether or not black-box fuzzers could
reveal real bugs and how effective was the \hi{}-\lo\ warning
classification.  We expected the number of warnings to increase
dramatically compared to the previous experiment and, if we realized
that the ratio of bugs from \lo\ warnings was rather low, we could
focus our inspection efforts on \hi\ warnings. To run this experiment,
we trained eight students in analyzing the warnings that our
infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
  from the Mozilla suite are often longer than others}. A bug report
was filed only after one of the authors reviewed the diagnosis. Each
student found at least one bug using this methodology.

\vspace{0.5ex}
\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial period of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning
belongs to the group of a given engine if only that engine manifests
distinct behavior, \ie{}, it produces a distinct output compared to
others. We separated in a distinct group the warnings for which two
engines diverge. The rationale for this methodology was to give
attention to each engine more uniformly, enabling more fair comparison
across engines.

@@

\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
assumption behind test set diversity is that faults often spread
contiguously in the input domain. Consequently, it should be
beneficial to partition the input domain and explore it more evenly as
to find bugs faster. Later in the nineties, Chen and
Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
the continuity assumption. They found that faults, most often,
manifest themselves in regular patterns across the input
domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
observations led researchers to investigate generalizations of the
approach to non-numerical data types and strategies to explore the
input (or output) space to solve different problems in Software
Engineering (\eg{}, test input generation and test
selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
paper explores diversity of sources of test cases and diversity of
engine implementations. We remain to investigate the diversity of test
cases themselves. In principle, that could help reduce the number of
alarms to inspect, for example.

@@

This paper reports on a study to evaluate two diversity-aware
techniques for finding bugs in \js{}--test transplantation and
cross-engine differential testing. The first technique explores
diversity of test sources; it runs the test suite of one given engine
in another engine. The second technique explores diversity of
implementations; it fuzzes existing inputs and then compares the
output produced by different engines with a differential oracle.

We found that both techniques were very effective at finding bugs in
\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
study. Of which, \totalBugsConfirmed\ were confirmed by developers and
\totalBugsFixed\ were fixed. Although more work is necessary to reduce
cost of manual analysis, we found that our results provide strong
evidence that exploring diversity should be encouraged to find
functional bugs in JavaScript engines.

>>>>

%\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
\title{New title}
%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head

@@

\begin{abstract}
  \input{abstract}
  %\keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
  \keywords{Test Transplantation \and Differential Testing \and JavaScript}
\end{abstract}

@@

%% WHAT WE DID
This work, which is empirical in nature, reports on a study to evaluate
the ability of two testing techniques to expose bugs in JavaScript engines.

%\vspace{-1ex}
%noitemsep,
\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
\item \emph{Test transplantation}. 
  This technique evaluates the effect of running test files
  written for a given engine in other engines. The intuition is that
  developers design test cases with different objectives in mind. As
  such, replaying these tests in different engines could reveal
  unanticipated problems.

\item \emph{Cross-engine differential testing}. 
  This technique fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines using a differential
  oracle. The intuition is that interesting inputs can be created
  from existing inputs and multiple engines can be used to address the
  lack of oracles.
\end{itemize}

@@

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
%\emph{Related Ideas.}~The idea of test set diversity dates back to the
%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
%to prior work on this topic, this paper explores diversity of
%implementations and diversity of sources of test cases as opposed to
%diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
%elaborates related work on this topic.
%
\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07} (DT) 
has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). Variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is empirical: 
we provide a comprehensive study analyzing the effectiveness of 
test transplantation and differential testing
in revealing functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed. 
We reported a total of \totalBugsReported{} bugs. 
Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed. 
2)~An infrastructure for performing test transplantation and differential testing.
The scripts to run the experiments will be available upon request. 
The data is publicly available \dataRepo{}.

\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
that exploring test transplantation and differential testing
should be encouraged to find functional bugs
in JavaScript engines.

@@

The goal of this paper is to assess ability of 
test transplantation and differential testing
to find functional bugs
in \javascript\ engines. Based on that, we pose three questions:
\begin{description}[leftmargin=.5in]
\item[RQ1.] How conformant are the engines to the Test262 suite?
\item[RQ2.] How effective is test transplantation to find bugs?
\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
\end{description}

The first question focuses on the conformance of our selected engines
to the official Test262 suite~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. The second question
focuses on the effectiveness of test transplantation
(Section~\ref{sec:transplantation}). The rationale for using inputs
from different engines is that developers consider different goals
when writing tests---suites written for a given engine may cover
scenarios not covered by a different engine. The third question
evaluates the effectiveness of cross-engine differential testing to
find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale for this question is that fuzzing inputs may explore
scenarios not well-tested by at least one of the engines.

@@

\vspace{0.5ex} \lbrack{}Exploratory Phase\rbrack{} For the first
three months of the study, our inspection process was exploratory.  In
this phase, we wanted to learn whether or not black-box fuzzers could
reveal real bugs and how effective was the \hi{}-\lo\ warning
classification.  We expected the number of warnings to increase
dramatically compared to the previous experiment and, if we realized
that the ratio of bugs from \lo\ warnings was rather low, we could
focus our inspection efforts on \hi\ warnings. To run this experiment,
we trained eight students in analyzing the warnings that our
infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
  from the Mozilla suite are often longer than others}. A bug report
was filed only after one of the authors reviewed the diagnosis. Each
student found at least one bug using this methodology.

\vspace{0.5ex}
\lbrack{}Non-Exploratory Phase\rbrack{} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial period of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning
belongs to the group of a given engine if only that engine manifests
distinct behavior, \ie{}, it produces a distinct output compared to
others. We separated in a distinct group the warnings for which two
engines diverge. The rationale for this methodology was to give
attention to each engine more uniformly, enabling more fair comparison
across engines.

@@

%\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
%The idea of test set diversity dates back to the
%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
%assumption behind test set diversity is that faults often spread
%contiguously in the input domain. Consequently, it should be
%beneficial to partition the input domain and explore it more evenly as
%to find bugs faster. Later in the nineties, Chen and
%Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
%the continuity assumption. They found that faults, most often,
%manifest themselves in regular patterns across the input
%domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
%observations led researchers to investigate generalizations of the
%approach to non-numerical data types and strategies to explore the
%input (or output) space to solve different problems in Software
%Engineering (\eg{}, test input generation and test
%selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
%paper explores diversity of sources of test cases and diversity of
%engine implementations. We remain to investigate the diversity of test
%cases themselves. In principle, that could help reduce the number of
%alarms to inspect, for example.

@@

This paper reports on a study to evaluate two
techniques for finding bugs in \js{}--test transplantation and
cross-engine differential testing. The first technique 
runs the test suite of one given engine in another engine. 
The second technique fuzzes existing inputs and then compares the
output produced by different engines with a differential oracle.

We found that both techniques were very effective at finding bugs in
\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
study. Of which, \totalBugsConfirmed\ were confirmed by developers and
\totalBugsFixed\ were fixed. Although more work is necessary to reduce
cost of manual analysis, we found that our results provide strong
evidence that exploring test transplantation and differential testing 
should be encouraged to find functional bugs in JavaScript engines.
